Manuscript plots

### 2023-12-15 manuscript_modelling_and_plots.Rmd
some added notes on how to calculate the conditional effects for each group

>>>>

## Conditional effects for each group

In the code chunk above (and the same for the gaze transitions entropy model), I am calculating the conditional effects for the existing groups in the dataset. I do this by extracting the model parameter estimates however in other tutorials (https://www.andrewheiss.com/blog/2021/11/10/ame-bayes-re-guide/#conditional-effects-for-existing-groups) they use a different method. Overall, the mean value of the conditional effect is identical. However in the Heiss tutorial, each estimate is accompanied by a 95% HDIs for each individual. This might prove useful for further analysis if needed, but it not used in the current manuscript.

To illustrate the equivalence, I'll use the Heiss method below.

```{r}
# Heiss method: we use the emmeans() function to calculate the posterior predictions across N-back and ppid (when lead vehicle == FALSE aka baseline), we set re_formula = NULL to include the influence of the random effects, and then contrast N-back TRUE-FALSE
heiss_example <- sge.fit.3 %>%
   emmeans(~ n_back + ppid,
           at = list(lead = FALSE,
                    ppid = levels(as.factor(entropy.total$ppid))),
          epred = TRUE, re_formula = NULL) %>% 
  contrast(method = "revpairwise", by = "ppid") %>% 
  gather_emmeans_draws()

# Because I am working with mean values with the model parameters, i use the mead_hdi() function
heiss_example %>% mean_hdi() %>%
  View()

# comparing the "ranef" column in "ppid.effects and the "value" column in "heiss_example. The values are exactly the same. 
```
